Use and acquisition of causal knowledge in a decision making process

### 2018-11-25 Propuesta/Presentacion/Presentacion_Corta.tex
Indice sin subsecciones

\begin{frame}[allowframebreaks]
\frametitle{Overview} % Table of contents slide, comment this block out to remove it
\tableofcontents % Throughout your presentation, if you choose to use \section{} and \subsection{} commands, these will automatically be printed on this slide as an overview of your presentation
\end{frame}

>>>>

\begin{frame}[allowframebreaks]
\frametitle{Contents} % Table of contents slide, comment this block out to remove it
\tableofcontents[hideallsubsections] % Throughout your presentation, if you choose to use \section{} and \subsection{} commands, these will automatically be printed on this slide as an overview of your presentation
\end{frame}

%
%\begin{frame}
%    \frametitle{Outline}
%    \begin{columns}[t]
%        \begin{column}{.3\textwidth}
%            \tableofcontents[sections={1-3}]
%        \end{column}
%        \begin{column}{.3\textwidth}
%            \tableofcontents[sections={4-5}]
%        \end{column}
%         \begin{column}{.3\textwidth}
%            \tableofcontents[sections={6-9}]
%        \end{column}
%    \end{columns}
%\end{frame}
